How to measure the radial velocity of a star:\\The invariant-spectrum case

### 2022-02-03 paper/main.tex
Updates from Overleaf

% to-do list
% ----------
% - Look for all instances of HOGG, MB, and CITE.
% - Make an acronym command and fix CLRB and all other acronyms.
% - Be sure to discuss SNR in a continuum resolution element, as well as in a pixel.
%.- Make sure that, for any assumption that is explicitly tested, the forthcoming test is mentioned when the assumption is introduced.
% - Are we clear that we exponentiate the model to get the true data expectation?
% - Are we consistent in our use of Doppler shift, radial velocity, and redshift and so on?
% - Are we sensible in our use of first person?

@@

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/data.png}
    \end{center}
    \caption{Several example toy-data spectra, generated according to the rules described in the main text.
    At each epoch the true spectrum has the same overall shape; the only differences from epoch to epoch are from Doppler-shift changes and shot noise.\label{fig:data}}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    [HOGG: NEED FIGURE HERE]
    \end{center}
    \caption{HOGG: Something that shows the CCF for one epoch, and a zoom in showing the parabola fit.\label{fig:ccf}}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    [HOGG: NEED FIGURE HERE]
    \end{center}
    \caption{HOGG: Something that shows the CCF RVs for all epochs, that they saturate the bound.\label{fig:ccfrvs}}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    [HOGG: NEED FIGURE HERE]
    \end{center}
    \caption{HOGG: Something that shows the binary-mask CCF RVs are terrible if naively optimized.\label{fig:bccfrvswrong}}
  \end{mdframed}
\end{figure}%
\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    [HOGG: NEED FIGURE HERE]
    \end{center}
    \caption{HOGG: Something that shows the binary-mask CCFs deliver good RVs when fit after the fact with a Gaussian function.\label{fig:bccfrvs}}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    [HOGG: NEED FIGURE HERE]
    \end{center}
    \caption{HOGG: Something that shows the empirical-spectrum CCFs deliver good RVs.\label{fig:empiricalrvs}}
  \end{mdframed}
\end{figure}

>>>>

% to-do list
% ----------
% - Look for all instances of HOGG, MB, and CITE.
% - Make an acronym command and fix CLRB and all other acronyms.
% - Be sure to discuss SNR in a continuum resolution element, as well as in a pixel.
%.- Make sure that, for any assumption that is explicitly tested, the forthcoming test is mentioned when the assumption is introduced.
% - Are we clear that we exponentiate the model to get the true data expectation?
% - Are we consistent in our use of Doppler shift, radial velocity, and redshift and so on?
% - Are we sensible in our use of first person?
% - Do we address the relationship between our tiny spectral segment and a full spectrograph? Get scalings. Etc.

@@

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/data.png}
    \end{center}
    \caption{Two example toy-data spectra, generated according to the rules described in the main text.
    At each epoch the true spectrum has the same overall shape; the only differences from epoch to epoch are from Doppler-shift changes and shot noise.\label{fig:data}}
  \end{mdframed}
\end{figure}
\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/datazoom.png}
    \end{center}
    \caption{A zoom in on one of the toy-data spectra. Shown are both the data (dark black step function) and the true spectral model (thin red smooth line). The data for this epoch is Doppler shifted relative to the model, which is at zero Doppler shift.\label{fig:datazoom}}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/ccf.png}
    \end{center}
    \caption{HOGG: Something that shows the CCF for one epoch, and a zoom in showing the parabola fit.\label{fig:ccf}}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/ccfrvs.png}
    \end{center}
    \caption{HOGG: Something that shows the CCF RVs for all epochs, that they saturate the bound.\label{fig:ccfrvs}}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/bccfrvswrong.png}
    \end{center}
    \caption{HOGG: Something that shows the binary-mask CCF RVs are terrible if naively optimized.\label{fig:bccfrvswrong}}
  \end{mdframed}
\end{figure}%
\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/bccfrvs.png}
    \end{center}
    \caption{HOGG: Something that shows the binary-mask CCFs deliver good RVs when fit after the fact with a Gaussian function.\label{fig:bccfrvs}}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/empiricalrvs.png}
    \end{center}
    \caption{HOGG: Something that shows the empirical-spectrum CCFs deliver good RVs.\label{fig:empiricalrvs}}
  \end{mdframed}
\end{figure}
